A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-09-02 ccgrid.tex
linting

\begin{figure}[h!]
    \caption{\textbf{Algorithm: }Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g. $N_t$ is size of the training set.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
    \EndWhile
    \State \textbf{Fit AFR Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
    \State \textbf{Return:} $S_{\theta}$
\end{algorithmic}
\end{figure}

@@

\subsection{AFR Models}
\label{survival_time}
Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.

@@

\subsection{AFR Models}

@@

\subsection{AFR Models}
\label{res:afr}
Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}. For building the AFR model, we used 75\% of the available data and withheld 25\% for verification. The concordance is both strong (>.5) and similar for all three AFR models and both the train and test sets. We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFR models. Fig.~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFR models. For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.
\input{plots/combined/aft_comparison}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
        \caption{ }
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
        \caption{}
    \end{subfigure}
    \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
    \label{fig:qq}
\end{figure*}
\begin{figure}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
        \caption{Coefficients of the Covariates for the Weibull AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
        \label{fig:aft}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
        \caption{Partial Effect  of device on $S_{\theta}(t)$ }
        \label{fig:partial}
    \end{subfigure}
    \caption{Weibull AFR Model.}
\end{figure}

>>>>

\begin{figure}[h!]
    \caption{\textbf{Algorithm: }Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x$ of size $N$, Parameters $\theta$, Loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and a number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, e.g. $N_t$ is size of the training set.
    \State \textbf{Initialize:} classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
    \EndWhile
    \State \textbf{Fit AFT Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
    \State \textbf{Return:} $S_{\theta}$
\end{algorithmic}
\end{figure}

@@

\subsection{AFT Models}
\label{survival_time}
Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts \cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time or $S_{\theta}(t)$. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.

@@

\subsection{AFT Models}

@@

\subsection{AFT Models}
\label{res:afr}
Table~\ref{tab:combined} shows the performance metrics for all three AFR models, as outlined in Sec.~\ref{survival_time}. For building the AFR model, we used 75\% of the available data and withheld 25\% for verification. The concordance is both strong (>.5) and similar for all three AFR models and both the train and test sets. We observed no more than 1\% mean absolute error in the probabilities (ICI) and no error in the median probability (E50) across all three AFR models. Fig.~\ref{fig:qq} depicts the observed and predicted probabilities for all three AFR models. For further analysis, we chose the Weibull AFR due to its superior fir in  Fig.~\ref{fig:qq}.
\input{plots/combined/aft_comparison}

@@

\begin{figure*}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/weibull_qq.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_logistic_qq.pdf}
        \caption{ }
    \end{subfigure}
    \begin{subfigure}[b]{.3\linewidth}
        \centering
        \includegraphics[width=\linewidth,clip]{plots/combined/log_normal_qq.pdf}
        \caption{}
    \end{subfigure}
    \caption{The red line depicts the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis). The dotted line depicts a perfect model.}
    \label{fig:qq}
\end{figure*}
\begin{figure}[h!]
    \centering
    \captionsetup[subfigure]{skip=0pt} % Adjust the skip here
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_aft.pdf}
        \caption{Coefficients of the Covariates for the Weibull AFR model. Here, "Random State" is used as a control variable that should be (and is) close to 0.}
        \label{fig:aft}
    \end{subfigure}
    \begin{subfigure}[b]{\linewidth}
        \centering
        \includegraphics[width=.6\linewidth,clip]{plots/combined/weibull_device_num_partial_effect.pdf}
        \caption{Partial Effect  of device on $S_{\theta}(t)$ }
        \label{fig:partial}
    \end{subfigure}
    \caption{Weibull AFT Model.}
\end{figure}
